Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2021-07-11 ms/Thesis/thesis.tex
Add (a) and (b) labels to figure 5 - time series
Add feuture work to the discussion

\begin{figure}[h]
  \centering       
    \includegraphics[scale=0.5]{../Figures/Unstable_Time_series.eps}
    \includegraphics[scale=0.5]{../Figures/Stable_Time_series.eps}
    \caption{\textbf{Unstable and stable equilibrium dynamics} 
    The figure shows the frequency of cooperation over time (generations) starting from different initial frequencies.
    In \textbf{(a)} the system has unstable equilibrium and therefore, all the curves are moving away from it.
    In \textbf{(b)} the system has stable equilibrium and therefore, all the curves moves towards it. 
    Here, $T_A = 0.5$, $c = 0.5$,  $v=0.59$ and \textbf{(a)} $T_B = 0.4$, $\alpha=0.1$ and $b=1.2$. \textbf{(b)} $T_B=0.7$, $\alpha=0.6$ and $b=2.3$.}
    \label{fig:time_series}
\end{figure}

@@

Another mechanism that was suggested by \citet{traxler2011social} showed that \emph{conditional cooperation} based on norm-dependent relational utilities, i.e. individual will only cooperate if it knows that others will cooperate too, can sustain cooperation in a community – provided that cooperation is already at a high level.
Unlike \emph{conditional cooperation}, interaction-transmission association can sustain cooperation in community even if cooperation is initially rare. 
\citet{morsky2020false} suggested that false beliefs on the frequencies of the cooperator can affect the individual decision whether to cooperate or not. If the individual over estimate the number of cooperators it will be more likely to cooperate. This flase belief can help sustain cooperation even if cooperartion is initially rare. 
% DC: Let's discuss this paragraph - is it good?

>>>>

\begin{figure}[h]
  \centering       
    \includegraphics[scale=0.5]{../PRSB_figures/fig_5.pdf}
    \caption{\textbf{Unstable and stable equilibrium dynamics} 
    The figure shows the frequency of cooperation over time (generations) starting from different initial frequencies.
    In \textbf{(a)} the system has unstable equilibrium and therefore, all the curves are moving away from it.
    In \textbf{(b)} the system has stable equilibrium and therefore, all the curves moves towards it. 
    Here, $T_A = 0.5$, $c = 0.5$,  $v=0.59$ and \textbf{(a)} $T_B = 0.4$, $\alpha=0.1$ and $b=1.2$. \textbf{(b)} $T_B=0.7$, $\alpha=0.6$ and $b=2.3$.}
    \label{fig:time_series}
\end{figure}

@@

Another mechanism that was suggested by \citet{traxler2011social} showed that \emph{conditional cooperation} based on norm-dependent relational utilities, i.e. individual will only cooperate if it knows that others will cooperate too, can sustain cooperation in a community – provided that cooperation is already at a high level.
Unlike \emph{conditional cooperation}, interaction-transmission association can sustain cooperation in community even if cooperation is initially rare. 
\citet{morsky2020false} suggested that false beliefs on the frequencies of the cooperator can affect the individual decision whether to cooperate or not. If the individual over estimate the number of cooperators it will be more likely to cooperate. This false belief can help sustain cooperation even if cooperartion is initially rare. 
% DC: Let's discuss this paragraph - is it good?

In this work, we have studied a cultural evolution model in which interactions are modeled as a prisoner's dilemma game.
We also assumed that in each generation individuals have only one meaningful interaction.
It would be interesting to investigate a model in which multiple games are played in each generation. 
This would make the model more realistic and more complicated to solve. To overcome the math complication, a numerical simulations can be used. 
The model can be further expand by changing the game to Stag Hunt game. \citet{tomasello2012two} claim that Stag Hunt game can better explain evolution of cooperation in humans. 
Humans often collobrate in Stag Hunt type situations in which all participants had alternatives but anticipated an even greater benefit from
successful capturing of the stag\citep{mitani2012evolution}.
